---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Siqi Zhao"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases, color = state)) + 
  geom_point() 
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA", race != "Total") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + 
  geom_smooth(method = "lm")+
  geom_point()
```

1. Write code for a plot and describe what you observe?
In state MA, white people have a fatest growth race. 
2. Are there any conclusions you can draw?
In the state MA, white people are easier to get covid. 
3. What were you not able to do due to not having the R knowledge?
Because there are huge data, without R, I cannot draw the plot of all the data. 
4. What other data would be useful to better understand this data?



```{r}
covid_data_long |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = count, color = race)) + 
  geom_point()
```


So focus on the white people in MA, the deaths 
```{r first_plot}
ggplot(filter(covid_data_orig,State == "MA") ) + 
  geom_point(aes(x = Date, y = Cases_White, color= "red")) +
  geom_point(aes(x = Date, y = Deaths_White, color= "green")) +
  geom_point(aes(x = Date, y = Hosp_White, color= "blue")) 
```

```{r first_plot}
ggplot(covid_data_count, aes(x = state, fill = state)) + 
  geom_bar() 
```

```{r}
covid_data_count_race = covid_data_count %>% group_by(covid_data_count$race)
ggplot(covid_data_count, aes(x = date, y = Cases), color = state)+
         geom_point()
```
